---
title: "Data"
author: "Miguel Conde"
date: "10 de mayo de 2017"
output:
  html_document:
    toc: true
    toc_float: true
    toc_depth: 4
    number_sections: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE,
                      fig.align = "center")
```

Europe 2020 Strategy sets out a vision of Europe's social market economy for the 21st century and notably retained the 3% R&D intensity goal as one of the five headline targets to be achieved by the EU by 2020.

# DATA

http://ec.europa.eu/eurostat/web/science-technology-innovation/data/main-tables

## Research and development expenditure, by sectors of performance - % of GDP

**Research and development expenditure, by sectors of performance - % of GDP**

**Short Description**: Research and experimental development (R&D) comprise creative work undertaken on a systematic basis in order to increase the stock of knowledge, including knowledge of man, culture and society, and the use of this stock of knowledge to devise new applications. 

R&D expenditures include all expenditures for R&D performed within the business enterprise sector (BERD) on the national territory during a given period, regardless of the source of funds. R&D expenditure in BERD are shown as a percentage of GDP (R&D intensity).

```{r}
source("readExcelData.R")
RD_Exp_GDP <- readExcel_RD_Exp_GDP("All Sectors")

RD_Exp_GDP <-
  array(data = c(unlist(readExcel_RD_Exp_GDP("All Sectors")[,-1]),
                 unlist(readExcel_RD_Exp_GDP("Business enterprise sector")[,-1]),
                 unlist(readExcel_RD_Exp_GDP("Government sector")[,-1]),
                 unlist(readExcel_RD_Exp_GDP("Higher education sector")[,-1]),
                 unlist(readExcel_RD_Exp_GDP("Private non-profit sector")[,-1])),
        dim = c(nrow(RD_Exp_GDP),
                ncol(RD_Exp_GDP)-1,
                5),
        dimnames = list(Country = RD_Exp_GDP$geo,
                        Year = 2004:2015,
                        Sector = c("AllS", "BES", "GS", "HES", "PNPS")))

head(RD_Exp_GDP[,,"AllS"])
```
```{r}
library(DT)
datatable(RD_Exp_GDP[,,"AllS"], 
          extensions = 'Buttons', 
          options = list(pageLength = 10,
                         columns = list(orederable = FALSE),
                         dom = 'Bfrtip',
                         buttons = c('copy', 'csv', 'excel', 'pdf', 'print')),
          caption = 'Table 1: All sectors Research and Development expenditure - % of GDP.\\(Source: Eurostat)')
```



```{r}
allS_mts <- ts(t(RD_Exp_GDP[,,"AllS"]),
               frequency = 1, start = c(2004,1))
allS_mts[, c("EU28", "Spain")]

```

```{r}
library(xtable)
xtable(allS_mts[, c("EU28", "Spain")])
```


```{r}
barplot(RD_Exp_GDP[,"2015",][,"AllS"])
```

```{r warning=FALSE}
library(highcharter)
hc <- highchart()

for(c in 1:ncol(allS_mts)) {
  hc <- (hc %>% hc_add_series_ts(allS_mts[, c], type = "line", 
                              name = colnames(allS_mts)[c]))
}

hc <- hc %>% hc_title(text = "Research and development expenditure, by sectors of performance - % of GDP")

hc
```

```{r}
myData <- as.data.frame(RD_Exp_GDP[,"2013", ])
myData <- myData[apply(myData, 1, function(x) sum(is.na(x[-1]))) < 4, ]
myData <- myData[order(myData$GS+myData$HES, decreasing = TRUE), ]
hc <- highchart()
hc <- hc %>% 
  hc_chart(type = "column",
           options3d = list(enabled = TRUE, beta = 15, alpha = 15)) %>% 
  hc_title(text = "2013 Research and development expenditure, by sectors of performance - % of GDP") %>% 
  # hc_yAxis(title = list(text = "Weights")) %>% 
  hc_plotOptions(column = list(
    dataLabels = list(enabled = FALSE),
    stacking = "normal",
    enableMouseTracking = TRUE)
  ) %>% 
  hc_add_series(name = "Business enterprise sector", data = myData[, "BES"])  %>%
  hc_add_series(name = "PNPS",                       data = myData[, "PNPS"]) %>%
  hc_add_series(name = "Government sector",          data = myData[, "GS"]) %>%
  hc_add_series(name = "Higher education sector",    data = myData[, "HES"])

hc <- (hc %>% hc_xAxis(categories = row.names(myData)))

hc
```

## Gross domestic expenditure on R&D (GERD) by source of funds - % of total GERD

**Gross domestic expenditure on R&D (GERD) by source of funds - % of total GERD**

**Short Description**: This table presents the relative shares of the different sources of funds in R&D. 

More specifically the indicators provided are percentage of GERD (Gross domestic expenditure on R&D) financed respectively by industry, government, the higher education and the private non profit sector. The fifth source of funds shown, which also make the breakdown complete, is GERD financed from abroad. 

R&D is an activity where there are significant transfers of resources between units, organisations, sectors and countries. 

The importance of the source of funding has been recognized in one of the Barcelona targets of the Lisbon agenda where it is said that the appropriate split for R&D is 1/3 financed by public funds and 2/3 by private.

```{r}
RD_pGERD <- readExcel_RD_pGERD("Business enterprise sector")

RD_pGERD <-
  array(data = c(unlist(readExcel_RD_pGERD("Business enterprise sector")[,-1]),
                 unlist(readExcel_RD_pGERD("Government sector")[,-1]),
                 unlist(readExcel_RD_pGERD("Higher education sector")[,-1]),
                 unlist(readExcel_RD_pGERD("Private non-profit sector")[,-1]),
                 unlist(readExcel_RD_pGERD("Abroad")[,-1])),
        dim = c(nrow(RD_pGERD),
                ncol(RD_pGERD)-1,
                5),
        dimnames = list(Country = RD_pGERD$geo,
                        Year = 2004:2015,
                        Sector = c("BES", "GS", "HES", "PNPS", "Abroad")))

head(RD_pGERD[,,"BES"])
```

```{r}
datatable(RD_pGERD[,,"BES"], 
          extensions = 'Buttons',
          options = list(pageLength = 10,
                         columns = list(orederable = FALSE),
                         dom = 'Bfrtip',
                         buttons = c('copy', 'csv', 'excel', 'pdf', 'print')),
          caption = 'Table 2: Business enterprise sector %GERD.\\(Source: Eurostat)')
```


```{r}
myData <- as.data.frame(RD_pGERD[,"2013", ])
myData <- myData[apply(myData, 1, function(x) sum(is.na(x))) < 5, ]
myData <- myData[order(myData$GS+myData$HES, decreasing = TRUE), ]
hc <- highchart()
hc <- hc %>% 
  hc_chart(type = "column") %>% 
  hc_title(text = "2013 Gross domestic expenditure on R&D (GERD) by source of funds - % of total GERD") %>% 
  # hc_yAxis(title = list(text = "Weights")) %>% 
  hc_plotOptions(column = list(
    dataLabels = list(enabled = FALSE),
    stacking = "normal",
    enableMouseTracking = TRUE)
  ) %>% 
  hc_add_series(name = "Abroad",                     data = myData[, "Abroad"]) %>%
  
  hc_add_series(name = "PNPS",                       data = myData[, "PNPS"]) %>%
  hc_add_series(name = "Business enterprise sector", data = myData[, "BES"]) %>%   hc_add_series(name = "Higher education sector",    data = myData[, "HES"]) %>%
  hc_add_series(name = "Government sector",          data = myData[, "GS"])
  
hc <- (hc %>% hc_xAxis(categories = row.names(myData)))

hc
```



# DATA SOURCES
http://uis.unesco.org/apps/visualisations/research-and-development-spending/
http://data.uis.unesco.org/Index.aspx?DataSetCode=SCN_DS&lang=en
http://data.worldbank.org/indicator/SP.POP.SCIE.RD.P6
http://data.worldbank.org/indicator/NY.GDP.PCAP.PP.CD
http://www.oecd.org/innovation/inno/researchanddevelopmentstatisticsrds.htm

